### 2025-08-10 chapters/benchmark.tex
minor grammatical modifications

This chapter provides a detailed empirical performance evaluation of a set of benchmark workloads executed within the Keystone enclave framework. The primary objective is to quantitatively assess the overheads and limitations introduced by enclave-based execution, focusing on how system-level parameters and hardware constraints influence workload behavior under trusted execution.

The evaluation covers a mix of general-purpose and cryptographic workloads. Specifically, we utilize the Dhrystone and CoreMark benchmarks, which are standard tools for measuring integer processing performance and embedded system efficiency, respectively. Additionally, the Kyber post-quantum cryptographic algorithm is included to evaluate a compute-intensive, security-critical workload relevant for future-proof cryptographic applications. This combination allows us to characterize enclave performance across a spectrum of computational patterns and resource demands.

>>>>

This chapter presents a detailed empirical evaluation of the Keystone enclave framework, with a specific focus on its performance characteristics under a range of representative workloads. The primary aim is to quantify the computational and system-level overheads introduced by secure enclave execution on RISC-V platforms, and to explore how these overheads are influenced by underlying hardware configurations and architectural constraints. By systematically comparing enclave-based execution against native (non-isolated) execution, we aim to identify the key trade-offs and limitations that developers and system architects must consider when adopting enclaves for trusted execution.

To achieve this, we deploy a carefully selected set of benchmark workloads that span both general-purpose and security-critical application domains. These include the Dhrystone and CoreMark benchmarks—commonly used to assess CPU performance and embedded system efficiency—as well as the Kyber post-quantum cryptographic algorithm, which provides a real-world workload with stringent security and computational requirements. Together, these benchmarks provide a diverse and comprehensive view of how Keystone enclaves behave across different execution contexts.

The benchmarking process is structured to examine four interrelated dimensions. First, we establish a native performance baseline to isolate the impact of enclave-related operations. Second, we evaluate the performance of the same workloads when executed within enclaves, highlighting the latency and resource costs incurred by isolation mechanisms such as Physical Memory Protection (PMP) and context switching. Third, we perform a workload sensitivity analysis, comparing the behavior of different benchmark types—sequential vs. parallel, lightweight vs. compute-intensive—to determine how workload characteristics affect enclave performance. Finally, we assess the influence of key hardware parameters, including CPU core count, memory size, and cache configuration, on both native and enclave execution.

Through these experiments, we uncover both expected and non-trivial behaviors. For instance, while enclave overheads are generally modest—typically under 15\%—they are highly sensitive to parallelism and memory access patterns. Furthermore, we identify critical bottlenecks, such as the fixed number of PMP entries available for isolating memory regions, which directly limit enclave concurrency and scalability.

The results presented in this chapter serve as the empirical foundation for the interpretive analysis in the next chapter. By rigorously characterizing the performance profile of Keystone enclaves, we establish a data-driven basis for understanding the broader implications of enclave deployment in secure system design, as well as informing practical strategies for optimization and resource management.

### 2025-08-10 chapters/discussion.tex
minor grammatical modifications

\section{Synthesis of Key Performance Trends}
This chapter integrates and interprets the empirical results obtained from benchmarking Keystone enclaves, offering a comprehensive synthesis of performance characteristics, limitations, and broader implications. The experimental data reveal several critical insights into the practicalities and challenges of enclave execution on RISC-V platforms, which have direct relevance to the design and deployment of secure computing systems.

First and foremost, enclave execution imposes non-negligible but moderate overheads compared to native, non-isolated execution. These overheads predominantly arise from the enforcement of memory isolation mechanisms, including Physical Memory Protection (PMP), and the additional context switches required to manage transitions between secure (enclave) and non-secure (host) execution states. Our results show that, across a diverse set of benchmarks ranging from general-purpose integer workloads to specialized cryptographic algorithms, overheads typically remain under 15%. However, this aggregate figure masks significant variability depending on workload type, degree of parallelism, and system configuration parameters such as CPU cores, memory allocation, and cache hierarchy.

A second major insight relates to the critical role of hardware-enforced resource constraints, specifically the limited number of PMP entries. The QEMU virt platform utilized in our experiments provides 16 PMP registers, which directly limits the number of isolated enclaves that can simultaneously operate. Attempts to instantiate more enclaves than PMP entries available result in immediate failure of enclave creation, as indicated by distinct Supervisor Binary Interface (SBI) error codes and kernel log messages. This finding underscores the fundamental impact of hardware architecture on enclave scalability and points to PMP capacity as a bottleneck that must be carefully managed in real-world systems.

Thirdly, workload characteristics strongly influence enclave performance overheads. Compute-bound, sequential workloads such as the Kyber post-quantum cryptographic algorithm experience comparatively low performance degradation within enclaves. This is consistent with Kyber’s minimal inter-thread communication and largely predictable memory access patterns. In contrast, highly parallelizable benchmarks like CoreMark exhibit increasing overhead with core count, reflecting the compounded costs of synchronization, enclave entry/exit transitions, and possibly contention in PMP configuration. This differential sensitivity implies that enclave performance optimization must be workload-specific, taking into account application parallelism and memory footprint.

Lastly, the interaction between resource allocation parameters—CPU cores, memory size, and cache configuration—and enclave performance is multifaceted. Increasing CPU cores yields diminishing returns beyond a threshold due to synchronization and enclave management overhead. Larger memory allocations improve performance primarily by reducing paging and improving cache locality but also can exacerbate PMP usage if memory regions are fragmented. Cache configuration impacts, though indirectly measured via QEMU’s system-wide cache model, suggest that optimizing cache size and associativity can mitigate enclave overheads, especially for instruction-intensive workloads. These observations highlight the necessity of a holistic approach to system tuning in enclave environments.

@@

In conclusion, while the PMP mechanism is undeniably a cornerstone of the Keystone security model, it also introduces a set of hard limitations that impact the practical deployment and scaling of enclaves. Understanding and addressing these limitations—both through hardware evolution and smarter software resource management—is essential for building scalable, secure computing platforms based on the RISC-V architecture.

>>>>

This chapter presents a critical analysis of the experimental findings discussed in the preceding chapters, with the goal of extracting deeper insights into the behavior, limitations, and practical consequences of enclave-based execution using the Keystone framework on RISC-V platforms. While the benchmarking results provide quantitative evidence of performance trends and system behavior, this chapter aims to interpret those findings in a broader architectural and systems-level context.

Specifically, we examine how various system parameters—such as CPU core count, memory configuration, cache hierarchy, and enclave workload characteristics—influence performance under isolation. We also discuss the architectural constraints imposed by RISC-V's Physical Memory Protection (PMP) mechanism, highlighting its central role in enforcing security while simultaneously acting as a scalability bottleneck. By analyzing the trade-offs between security guarantees and system throughput, we offer a nuanced understanding of the design space that system architects and security engineers must navigate when deploying enclaves in resource-constrained or high-concurrency environments.

In addition to synthesizing the key performance trends, this chapter explores the broader implications of enclave deployment for secure system design, particularly in scenarios involving cryptographic workloads, multi-tenant execution, and edge computing platforms. We assess the extent to which Keystone and PMP-based isolation mechanisms can be reliably scaled, and we consider practical strategies for overcoming current limitations through architectural or software-level optimizations.

Finally, the chapter concludes by formulating design recommendations and identifying future directions for research and development. These include enhancements to hardware features such as PMP flexibility, improved enclave management strategies at the software layer, and potential extensions to the Keystone framework to support more scalable and efficient trusted execution environments.

This chapter transitions from measurement to meaning: it connects the observed data to the architectural principles underpinning enclave execution, thereby informing both future research and practical deployment of secure computing systems based on open RISC-V architectures.

\section{Synthesis of Key Performance Trends}

A key observation from the evaluation is that enclave execution introduces moderate but measurable overheads relative to native, non-isolated execution. These overheads primarily stem from two factors: the enforcement of memory isolation through Physical Memory Protection (PMP), and the additional control flow transitions between enclave and host contexts. Across a range of benchmark scenarios—including general-purpose integer computations and cryptographic workloads—the performance penalty typically remains below 15\%. However, this aggregate figure conceals significant variance, which is highly dependent on workload characteristics, system architecture, and execution configuration. Variables such as the number of processor cores, memory availability, and cache configuration exert a substantial influence on the observed overhead.

A second and arguably more fundamental insight concerns the limitations imposed by hardware-enforced resource constraints, particularly the finite number of PMP entries. In the QEMU \texttt{virt} platform used for this study, the system supports a maximum of 16 PMP entries. Each enclave requires at least one such entry to define a protected memory region. This architectural constraint creates a hard upper bound on the number of enclaves that can be concurrently instantiated. When this limit is exceeded, enclave creation fails deterministically, with the system reporting specific Supervisor Binary Interface (SBI) error codes and kernel log messages. This result highlights a critical bottleneck for enclave scalability that arises not from software inefficiencies, but from underlying hardware design choices. In practical deployments—particularly in multi-tenant or concurrent environments such as edge nodes or confidential cloud computing platforms—PMP exhaustion could severely limit system utility unless proactively mitigated.

The analysis further reveals that enclave performance is highly sensitive to workload type. Sequential, compute-bound tasks such as the Kyber post-quantum cryptographic algorithm exhibit relatively low performance degradation when executed within an enclave. This is attributable to Kyber’s predictable memory access patterns and minimal need for inter-thread synchronization. By contrast, parallelizable workloads like CoreMark demonstrate increasing overhead as core count rises, driven by factors such as synchronization costs, increased enclave context switching, and potential contention in PMP entry allocation. These results suggest that enclave performance optimization must be workload-aware, with particular consideration given to application parallelism and memory behavior.

Finally, the relationship between system resource allocation—specifically CPU cores, memory capacity, and cache hierarchy—and enclave performance is nuanced. Increasing the number of processor cores beyond a certain threshold yields diminishing performance returns due to synchronization overhead and enclave management complexity. While increasing memory allocation generally improves performance by reducing page faults and improving cache locality, it may also exacerbate PMP usage if memory regions are fragmented. Although QEMU provides only a high-level approximation of cache behavior, the observed trends suggest that cache size and associativity can significantly influence enclave performance for instruction- and memory-intensive workloads. These interdependencies underscore the need for a holistic, system-level tuning approach when deploying TEEs in real-world scenarios.

The benchmarking results confirm that Keystone enclaves, while effective at enforcing isolation, require careful system configuration and architectural awareness to ensure scalable and efficient performance. The findings serve as a foundation for both immediate system tuning and future architectural innovation aimed at overcoming the current limitations of enclave-based trusted execution on RISC-V.

@@

While the PMP mechanism is undeniably a cornerstone of the Keystone security model, it also introduces a set of hard limitations that impact the practical deployment and scaling of enclaves. Understanding and addressing these limitations—both through hardware evolution and smarter software resource management—is essential for building scalable, secure computing platforms based on the RISC-V architecture.

### 2025-08-10 chapters/system-architecture.tex
updated TOC
minor grammatical modifications

\chapter{System Architecture and Design}
\label{chap:methodology}

@@

\section{Experimental Setup}
\label{sec:experimental-setup}

@@

\section{Kyber in the Enclave}
\label{sec:kyber-enclave}

@@

\section{Benchmarking tools and metrics}
\label{sec:benchmarking-tools}

@@

\section{Parameter Variation Strategy}
\label{sec:param-variation}

To investigate the architectural impact on enclave execution, this study systematically varied system parameters including memory size, core count, execution mode (sequential vs parallel), and cache configurations using QEMU’s cache modeling capabilities. The aim was to understand how these factors influence the behavior of trusted and non-trusted workloads under different resource constraints.

Cache simulation was conducted using the QEMU TCG plugin framework \cite{mandour2021cache}, which models per-core instruction and data caches in an idealized fashion. While this plugin is not cycle-accurate and does not isolate enclave-specific behavior, it enables consistent modeling of cache accesses and miss patterns across the entire QEMU runtime. This was sufficient to observe cache-related effects caused by workload behavior in different configurations.

To avoid excessive experimental overhead and redundant trends, five representative system configurations were selected. These were chosen to cover a wide range of memory capacities, CPU core counts, and execution modes. Each configuration enables a specific type of insight, ensuring a diverse but manageable evaluation matrix.

\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|c|p{7.5cm}|}
\hline
\textbf{Config Name} & \textbf{RAM} & \textbf{Cores} & \textbf{Execution} & \textbf{Rationale} \\
\hline
Low-End Baseline     & 64M         & 1             & Sequential         & Serves as the minimal configuration to establish baseline performance. Useful for understanding enclave overhead under tight resource constraints. \\
\hline
Balanced Parallel    & 128M        & 2             & Parallel           & Captures early-stage multicore scaling behavior. Highlights effects of light parallelism under modest memory availability. \\
\hline
Mid-Range Sequential & 256M        & 4             & Sequential         & Enables evaluation of scaling effects due to additional cores and memory, while keeping execution sequential to avoid parallel noise. \\
\hline
High-End Parallel    & 512M        & 6             & Parallel           & Represents a well-provisioned system where both memory and core resources are sufficient. Useful for observing near-ideal parallel execution. \\
\hline
Max Capacity Stress  & 2G          & 10            & Parallel           & Tests the upper bounds of simulated platform capacity. Helps identify performance saturation and the point of diminishing returns. \\
\hline
\end{tabular}
\caption{Summary of representative configurations used in performance evaluation.}
\end{table}

Several other configurations—such as single-core setups with excessive memory or high-core setups with limited memory—were explored during preliminary testing. However, they offered little additional insight beyond what was observable in the selected set. For instance, excessive memory on a single core often led to underutilization, while many-core systems with small memory pools frequently resulted in excessive context switching. Both behaviors were captured effectively by existing selected configurations.

Across all system configurations, three cache profiles were tested: a baseline setup with 8\,KB 4-way LRU caches, a larger 32\,KB 8-way configuration, and a fixed-size cache using FIFO and random eviction strategies. A consistent block size of 64 bytes was used to preserve spatial locality. Although the cache plugin logs system-wide activity, observed trends were analyzed in conjunction with benchmark behavior to infer their likely contributions to overall performance variation.

Benchmarks were run in both native and enclave execution modes to enable direct comparisons. This design facilitated the isolation of architectural performance trends and the specific overhead introduced by trusted execution.

\section{Data Collection and Analysis Procedures}
\label{sec:data-collection}

All benchmarks were executed within a consistent virtualized RISC-V environment using QEMU. For each selected configuration, both Dhrystone and CoreMark benchmarks were run in native and enclave modes to capture the impact of enclave isolation under different resource and cache conditions.

Each experiment consisted of ten executions. To reduce variance caused by warm-up behavior, the first run was discarded, and the remaining nine were used to compute average performance. Key performance metrics included total wall-clock execution time, benchmark throughput (DMIPS or iterations/sec), and standard deviation.

In addition to these primary measurements, system-level runtime statistics were collected from within the guest Linux environment. These included:

\begin{itemize}
    \item User and system CPU time
    \item Maximum memory usage (RSS)
    \item Minor and major page faults
    \item Voluntary and involuntary context switches
\end{itemize}

These metrics were essential to understanding how different system configurations affected workload behavior. For example, high numbers of involuntary context switches in parallel configurations often indicated memory contention or over-subscription of CPU cores.

Cache-related metrics were gathered using the QEMU cache plugin, which logs all instruction and data cache accesses and misses at the system level. Although enclave-specific cache statistics could not be isolated, the relative trends between native and enclave executions under identical configurations allowed for meaningful comparative analysis.

Performance overhead introduced by enclave execution was quantified using the percentage increase in execution time compared to native mode, calculated as:

@@

This normalized metric enabled consistent cross-comparison between configurations with vastly different execution baselines.

All benchmark scripts, plugin configurations, and raw logs were version-controlled and archived. Detailed plugin output, configuration parameters, and system call traces are provided in Appendix~\ref{appendix:cache-plugin} for transparency and reproducibility.

>>>>

\chapter{System Design and Methodology}
\label{chap:methodology}

@@

\section{Experimental Platform and Environment}
\label{sec:experimental-setup}

@@

\section{Integration of Kyber into Keystone}
\label{sec:kyber-enclave}

@@

\section{Benchmarking Suite and Metrics}
\label{sec:benchmarking-tools}

@@

\section{Parameter Configuration and Variation}
\label{sec:param-variation}

To rigorously assess how architectural and system-level parameters influence the performance of workloads executed within secure enclaves, this study undertook a systematic exploration of configurable runtime characteristics on the simulated RISC-V platform. Specifically, we varied four principal dimensions: physical memory size, the number of processor cores, execution mode (sequential versus parallel), and cache configuration. These parameters were chosen based on their known relevance to workload performance and enclave behavior, and were adjusted within the bounds of what is supported by the QEMU-based virtual platform and the Keystone framework.

The overarching objective of this variation was to uncover the extent to which system-level constraints and resource allocations impact both trusted (enclave) and non-trusted (native) execution. By exploring diverse configurations, we aimed to characterize how resource limitations (e.g., constrained memory or limited cores) manifest in performance degradation, and to what degree secure execution amplifies or mitigates these effects.

To simulate cache behavior, we employed the QEMU TCG plugin framework, specifically leveraging the cache modeling capabilities introduced by Mandour et al. \cite{mandour2021cache}. This plugin facilitates the modeling of per-core instruction and data caches and enables the collection of aggregate system-wide cache statistics. While it does not provide cycle-accurate timing nor isolate enclave-specific cache behavior, its ability to log cache access and miss patterns uniformly across all benchmark executions proved sufficient for analyzing cache-related effects in both secure and non-secure modes. The insights gleaned from this analysis, though approximate, were instrumental in identifying general cache utilization trends under various workloads and resource configurations.

Given the expansive parameter space created by the combination of memory size, core count, execution mode, and cache settings, it was neither practical nor necessary to exhaustively benchmark every possible configuration. Instead, we curated a set of five representative system configurations that collectively span a meaningful range of the performance spectrum—from minimal, resource-constrained environments to well-provisioned, multicore systems operating at near full capacity. These configurations are detailed in Table~\ref{tab:configurations}.

\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|c|p{7.5cm}|}
\hline
\textbf{Config Name} & \textbf{RAM} & \textbf{Cores} & \textbf{Execution} & \textbf{Rationale} \\
\hline
Low-End Baseline     & 64M         & 1             & Sequential         & Serves as a minimal configuration, enabling the establishment of baseline performance under constrained conditions. Useful for measuring the raw impact of enclave mechanisms in resource-starved environments. \\
\hline
Balanced Parallel    & 128M        & 2             & Parallel           & Captures early-stage scaling behavior with modest multicore setups. Helps isolate the overhead introduced by enclave entry/exit in light parallel workloads. \\
\hline
Mid-Range Sequential & 256M        & 4             & Sequential         & Provides a view into how increasing core count and memory capacity affect performance in the absence of thread-level parallelism. Useful for understanding system scalability independent of synchronization effects. \\
\hline
High-End Parallel    & 512M        & 6             & Parallel           & Represents a robust configuration where memory and cores are sufficiently provisioned. Designed to observe near-ideal parallel execution and potential scalability limits of the enclave framework. \\
\hline
Max Capacity Stress  & 2G          & 10            & Parallel           & Pushes the simulated platform to its upper bounds. Intended to explore saturation points, resource contention, and diminishing returns under heavy system load. \\
\hline
\end{tabular}
\caption{Summary of representative configurations used in performance evaluation.}
\label{tab:configurations}
\end{table}

In preliminary testing, a number of alternative configurations were explored to validate the diversity and coverage of the selected set. These included scenarios such as single-core systems with excessively large memory allocations and many-core setups with highly constrained memory. However, these combinations typically resulted in either underutilized resources or pathological behavior (e.g., excessive paging or context switching), without contributing new insight beyond what was captured by the five chosen profiles. For example, increasing memory size on a single-core system had negligible impact due to CPU-bound bottlenecks, while increasing core counts in systems with limited memory often led to high levels of involuntary context switching and scheduling overhead.

In addition to varying core and memory resources, three distinct cache configurations were tested across all system profiles to assess the sensitivity of enclave and native workloads to cache architecture. These configurations included:

\begin{itemize}
    \item A baseline setup featuring 8\,KB, 4-way set-associative caches with an LRU replacement policy
    \item An enlarged cache with 32\,KB size and 8-way associativity, reflecting more generous cache resources
    \item A fixed-size cache using FIFO and random eviction policies to model alternative eviction behaviors
\end{itemize}

All configurations used a consistent block size of 64 bytes to preserve spatial locality across workloads. Although the cache modeling plugin captures system-wide statistics and does not differentiate between enclave and non-enclave activity, observed trends—such as shifts in cache miss rates and access patterns—were analyzed in conjunction with benchmark-level behavior to infer their contribution to observed performance variations.

To enable direct and consistent comparisons, each benchmark was executed in both native and enclave modes under every configuration. This mirrored design allowed for clear isolation of the performance penalties introduced by enclave execution and helped disentangle architectural effects from security-related overhead.

\section{Data Collection and Reproducibility}
\label{sec:data-collection}

To ensure the integrity, consistency, and scientific validity of the performance evaluation, all benchmark experiments were conducted within a tightly controlled and reproducible virtualized environment. The entire measurement campaign was executed on a simulated RISC-V platform using the QEMU emulator, which served as the foundation for both native and enclave-based workloads. This consistent virtualization layer eliminated hardware variability and allowed for precise control over system resources such as memory, core count, and cache characteristics.

Each system configuration, as defined in Section~\ref{sec:param-variation}, was evaluated using the Dhrystone, CoreMark, and Kyber benchmarks. For each benchmark, tests were run in both native (non-enclave) and enclave execution modes to facilitate direct comparative analysis of performance overheads introduced by trusted execution.

To reduce transient measurement noise and improve the robustness of collected data, each benchmark experiment was repeated ten times per configuration. The first execution was discarded in all cases to account for initialization artifacts such as dynamic binary translation warm-up and memory allocation caching within the QEMU runtime. The remaining nine runs were averaged to produce stable and representative performance figures. In addition to computing the arithmetic mean, the standard deviation was recorded to provide a measure of variability across runs.

The primary performance metric collected was **total wall-clock execution time**, as measured from within the guest Linux environment using high-resolution timers (e.g., \texttt{clock\_gettime()}) or the Keystone timer API in enclave mode. For Dhrystone and CoreMark, benchmark-specific throughput metrics were also recorded, including Dhrystone MIPS (DMIPS) and iterations per second. These allowed for workload-specific efficiency comparisons across configurations.

In addition to these high-level metrics, detailed system-level runtime statistics were gathered using standard Linux facilities such as the \texttt{/proc} filesystem and the \texttt{getrusage()} system call. These included:

\begin{itemize}
    \item \textbf{User and system CPU time:} Total time spent in user-space and kernel-space respectively.
    \item \textbf{Maximum resident set size (RSS):} Peak memory consumption during execution.
    \item \textbf{Page fault statistics:} Number of minor (soft) and major (hard) page faults incurred during the benchmark.
    \item \textbf{Context switching behavior:} Number of voluntary and involuntary context switches, indicating scheduling and synchronization overhead.
\end{itemize}

These runtime indicators were critical in diagnosing performance behaviors that could not be attributed to CPU throughput alone. For instance, elevated context switch counts in parallel configurations were often correlated with increased enclave transition overhead or CPU oversubscription, especially in memory-constrained environments.

Cache-related metrics were obtained using the QEMU TCG plugin cache model described earlier. This plugin logs all instruction and data cache accesses and cache misses at the system level. While the plugin lacks enclave-specific visibility and does not model hardware-specific cache timing, it provides a consistent and useful proxy for analyzing trends in memory access behavior. Cache metrics were aligned with benchmark execution phases to identify correlations between cache activity and observed performance shifts.

To compute the enclave-specific performance overhead, we employed a normalized overhead metric defined as the relative increase in execution time between enclave and native modes:

@@

This percentage-based formulation allows for direct cross-comparison of overheads across workloads with differing baseline durations. It also facilitates trend identification across system configurations, particularly when assessing scaling behaviors.

For reproducibility, all benchmarking scripts, system configurations, QEMU command-line options, Keystone runtime parameters, and cache plugin settings were version-controlled using Git. Raw benchmark outputs, kernel logs, and cache plugin trace files were archived and documented. A complete snapshot of the experimental infrastructure, along with scripts to regenerate results, is provided in Appendix~\ref{appendix:cache-plugin}. This archival effort ensures that all reported results can be independently verified and reproduced by future researchers or evaluators.

\begin{figure}[H]
\centering
\begin{tikzpicture}[node distance=1.75cm]
\node (start)   [process] {Start: Define Benchmark Set};
\node (config)  [process, below of=start] {Select Hardware Configuration};
\node (native)  [process, below of=config] {Run Benchmarks in Native Mode};
\node (enclave) [process, below of=native] {Run Benchmarks in Enclave Mode};
\node (metrics) [process, below of=enclave] {Collect Performance Metrics};
\node (analyze) [process, below of=metrics] {Compare and Analyze Overheads};
\node (end)     [process, below of=analyze] {Store Logs and Archive Results};

\draw [arrow] (start)   -- (config);
\draw [arrow] (config)  -- (native);
\draw [arrow] (native)  -- (enclave);
\draw [arrow] (enclave) -- (metrics);
\draw [arrow] (metrics) -- (analyze);
\draw [arrow] (analyze) -- (end);
\end{tikzpicture}
\caption{Benchmarking and Data Collection Workflow}
\label{fig:benchmarking-workflow}
\end{figure}

\begin{figure}[H]
\centering
\begin{tikzpicture}[
    native/.style={draw, fill=blue!20, minimum width=1.2cm, minimum height=1cm, font=\small, rounded corners=2pt},
    enclave/.style={draw, fill=red!20, minimum width=1.2cm, minimum height=1cm, font=\small, rounded corners=2pt},
    label/.style={font=\bfseries, align=center},
    cell/.style={draw, minimum width=1cm, minimum height=0.6cm},
    every node/.style={inner sep=2pt}
]

% Column labels
\node[label] at (2.4, 6.2) {Low-End};
\node[label] at (4.4, 6.2) {Balanced};
\node[label] at (6.4, 6.2) {Mid-Range};
\node[label] at (8.4, 6.2) {High-End};
\node[label] at (10.4, 6.2) {Max Capacity};

% Row labels
\node[label, rotate=90] at (1, 5) {Dhrystone};
\node[label, rotate=90] at (1, 3) {CoreMark};
\node[label, rotate=90] at (1, 1) {Kyber};

% Dhrystone row
\node[native] at (2, 5) {11.3s};
\node[enclave] at (2.8, 5) {123s};

\node[native] at (4, 5) {107s};
\node[enclave] at (4.8, 5) {99s};

\node[native] at (6, 5) {91s};
\node[enclave] at (6.8, 5) {55s};

\node[native] at (8, 5) {22s};
\node[enclave] at (8.8, 5) {11s};

\node[native] at (10, 5) {5s};
\node[enclave] at (10.8, 5) {20s};

% CoreMark row (empty placeholders for now)
\foreach \x in {2,4,6,8,10} {
    \node[native] at (\x, 3) {};
    \node[enclave] at (\x+0.8, 3) {};
}

% Kyber row (empty)
\foreach \x in {2,4,6,8,10} {
    \node[native] at (\x, 1) {};
    \node[enclave] at (\x+0.8, 1) {};
}

% Native / Enclave labels inside or above boxes if needed
\node[font=\scriptsize] at (1.8, 5.8) {Native};
\node[font=\scriptsize] at (2.6, 5.8) {Enclave};

% Legend
\node[draw, fill=blue!20, minimum width=0.8cm, minimum height=0.6cm] at (6, -0.8) {};
\node at (6.9, -0.8) {Native};

\node[draw, fill=red!20, minimum width=0.8cm, minimum height=0.6cm] at (8.5, -0.8) {};
\node at (9.4, -0.8) {Enclave};

\end{tikzpicture}
\caption{Experiment Matrix: Benchmarks Across Configurations and Execution Modes}
\label{fig:experiment-matrix}
\end{figure}

### 2025-08-10 main.tex
reorganised key sections
changed verbatim to lstlistings
minor grammatical modifications

\documentclass[english, version-2020-11]{uzl-thesis}
\UzLStyle{pagella contrast design}
\usepackage{comment}
\usepackage{float}

@@

\include{chapters/methodology.tex}

\include{chapters/results.tex}

\include{chapters/recommendations.tex}

>>>>

\documentclass[english, version-2020-11]{uzl-thesis}
\UzLStyle{pagella contrast design}
\usepackage{comment}
\usepackage{float}
\lstset{basicstyle=\ttfamily}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows.meta, positioning, shadows.blur}

\tikzstyle{process} = [
    rectangle, rounded corners,
    minimum width=4.2cm,
    minimum height=1.2cm,
    text centered,
    draw=black,
    fill=blue!10,
    font=\sffamily\small,
    blur shadow
]

\tikzstyle{arrow} = [
    thick,
    ->,
    >=Stealth,
    draw=gray!80
]

\tikzstyle{cell} = [rectangle, draw=black, minimum width=2.5em, minimum height=2.5em, anchor=center]
\tikzstyle{native} = [cell, fill=blue!20]
\tikzstyle{enclave} = [cell, fill=red!20]
\tikzstyle{label} = [font=\bfseries]

@@

\include{chapters/system-architecture.tex}

\include{chapters/benchmark.tex}

%\include{chapters/results.tex}

\include{chapters/discussion.tex}

%\include{chapters/recommendations.tex}
